Formalizing Stack Safety as a Security Property

### 2023-02-02 submission5/core.tex
pass through formalism

\author{
  \IEEEauthorblockN{
    Sean Noble Anderson
  }
  \IEEEauthorblockA{
    Portland State University\\
    ander28@pdx.edu\\
  }
  \and
  \IEEEauthorblockN{
    Leonidas Lampropoulos
  }
  \IEEEauthorblockA{
    University of Maryland, College Park\\
    leonidas@umd.edu\\
  }
  \and
  \IEEEauthorblockN{
    Roberto Blanco
  }
  \IEEEauthorblockA{
    Max Planck Institute for Security and Privacy\\
    roberto.blanco@mpi-sp.org\\
  }
  \linebreakand
  \IEEEauthorblockN{
    Benjamin C. Pierce
  }
  \IEEEauthorblockA{
    University of Pennsylvania\\
    bcpierce@cis.upenn.edu\\
   }
  \and
  \IEEEauthorblockN{
    Andrew Tolmach
  }
  \IEEEauthorblockA{
    Portland State University\\
    tolmach@pdx.edu\\
  }
}

@@

\section{Machine and Security Semantics, Formally}
\label{sec:machine}

@@

The building blocks of a machine are {\em words} and {\em registers}.
Words are ranged over by \(\word\) and, when used as addresses, \(\addr\),
and are drawn from the set \(\WORDS\).
Registers in the set \(\REGS\) are ranged over by \(\reg\), with the stack pointer
given the special name \(\SP\);
some registers may be classified as caller-saved or callee-saved.
Along with the program counter, \(\PCname\), these are referred to as
{\em state elements} \(\component\) in the set \(\COMPONENTS ::= \PCname | \WORDS | \REGS\).

A {\em machine state} \(\mach \in \MACHS\) is a map from state elements to a set \(\mathcal{V}\) of
\emph{values},  with a step function \(\mach \xrightarrow{\bar{\psi},\obs} \mach'\).
Each value \(v\) contains a \emph{payload} word, written \(|v|\).
The details of value structure depend on the specific machine being modelled;
intuitively, the payload represents the part of the value that is relevant to
the behavior of the basic machine, while the rest of the value may contain
information relevant to a hardware enforcement mechanism (such as a tag).
We write \(\mach[\component]\) to denote the value of \(\mach\) at
\(\component\)  and \(\mach[v]\) as shorthand for \(\mach[|v|]\).

Security classes are ranged over by \(l \in \{\public, \object, \sealed, \unsealed\}\).
For some security class \(l\), we write \(l(V)\)
to denote the set of elements \(\component\) such that \(V ~ \component = l\).
The {\it initial view} \(V_0\) maps all stack locations to \(\unsealed\),
all other locations to \(\public\), and registers based on which set they
belong to: \(\sealed\) for callee-saved, \(\unsealed\) for caller-saved, and \(\public\) otherwise.

A {\it context} is a pair of the current activation's view and
a list of views representing the call stack (pending inactive
principals), ranged over by \(\sigma\).

A view \(V\) maps elements to security classes, and a context consists of the
view of the active function together with a stack of inactive views.
The initial context is \(\context_0 = (V_0, \emplist)\).
%
\[\context \in \CONTEXTS ::= \mathit{VIEW \times list ~ VIEW}\]
%
We have described informally how the security context develops as the system performs
security-relevant operations. Formally, we combine each machine state with a context
to create a {\it combined state} \(s = (\mach,\context)\) and a lift the transition
to \(\stepstounder{}\) on combined states, labeled with the same operations.
with each step, the context updates based on the function
\(Op : \MACHS \rightarrow \CONTEXTS \rightarrow \psi \rightarrow \CONTEXTS\).
Note that \(Op\) takes as its first argument the state {\it before} the step.
Since a single step might correspond to multiple operations, we apply
\(Op\) as many times as is needed.

@@

The definition of \(Op\) is most convenient to present decomposed into
rules for each operation. We have already seen the intuition behind the rules for
\(\mathbf{alloc}\), \(\mathbf{call}\), and \(\mathbf{ret}\).
For the machine described in the example, the \(Op\) rules would be those
found in \cref{fig:basicops}.

@@

We write the trace of execution from a state up to the first
state below depth \(d\) via the \(\hookrightarrow\) operator, defined coinductively.
When \(d = 0\), the trace will always be infinite. In this case we
omit \(d\) and just write \(\hookrightarrow s\).

@@

Two event traces $\obsT_1$ and $\obsT_2$ are {\em similar},
written \(\obsT_1 \eqsim \obsT_2\), if the sequence of non-silent events
is the same. That is, we compare up to deletion of \(\tau\) events.

@@

\section{Formal properties}
\label{sec:props}

Now we are ready to introduce the formal properties that define correctly enforced
security semantics. First, we must give a few prelimaries: the generation and comparison
of traces, variant states, and ``on-return'' assertions.

For a given system, we assume a \emph{compatibility} equivalence relation \(\sim\) on values.
Values are compatible if their tags (or whatever other data is important to
the machine's security enforcement mechanism) are identical,
even though their payloads may differ.
Two states are variants with respect to a set of elements \(\components\)
if they agree on the value of every element not in \(\components\) and
and have compatible values for every element in \(\components\).
Our notion of non-interference involves comparing the traces of such
\(\components\)-variants. We use this to define sets of irrelevant elements,
and secrets in general.

\definition Machine states \(\mach\) and \(\nach\) are {\em \(\components\)-variants},
written \(\mach \approx_\components \nach\), if, for
all \(\component \not \in \components\), \(\mach[\component] = \nach[\component]\)
and for all \(\component \in \components\), \(\mach[\component] \sim \nach[\component]\).

\definition An element set \(\components\) in state \((\mach,\context)\) contains
irrelevant values, written \((\mach,\context) \parallel \components\), if for all
\(\nach\) such that \(\mach \approx_{\components} \nach\),
\(\hookrightarrow (\mach,\context)  \eqsim \hookrightarrow (\nach,\context)\).

\definition \(\Delta(\mach,\mach')\) is the set of elements \(\component\)
such that \(\mach[\component] \not = \mach'[\component]\).

@@

Conceptually, the corrupted set treats \(\mach\) and \(\nach\) as initial states whose
and \(\mach'\) and \(\nach'\) as their corresponding final states, such that any element
that has changed from its initial value but does not match between the final states
is considered to have propagated some varied data from the original pair.

@@

\judgmenttwobrlong[Step]
                  {\(|\sigma| \geq d\)}
                  {\((d \uparrow P) ~ (\mach', \context')\)}
                  {\((\mach, (V,\sigma)) \stepstounder{\overline{\psi}} (\mach', \context',\obs)\)}
                  {\((d \uparrow P) ~ (\mach, (V,\sigma))\)}

@@

\judgmenttwobrlong[Left]
                  {\(|\sigma_1| \geq d\)}
                  {\((\mach_1,(V_1,\sigma_1)) \stepstounder{\overline{\psi}} (\mach_1',\context_1',\obs)\)}
                  {\((\mach_1',\context_1') ~ (d \Uparrow R) ~ (\mach_2,(V_2,\sigma_2))\)}
                  {\((\mach_1,(V_1,\sigma_1)) ~ (d \Uparrow R) ~ (\mach_2,(V_2,\sigma_2))\)}

\judgmenttwobrlong[Right]
                  {\(|\sigma_2| \geq d\)}
                  {\((\mach_2,(V_2,\sigma_2)) \stepstounder{\overline{\psi}} (\mach_2',\context_2',\obs)\)}
                  {\((\mach_1,(V_1,\sigma_1)) ~ (d \Uparrow R) ~ (\mach_2,\context_2')\)}
                  {\((\mach_1,(V_1,\sigma_1)) ~ (d \Uparrow R) ~ (\mach_2,(V_2,\sigma_2))\)}

Finally, we can define our core properties. They can be found in \cref{tab:props},
arranged to show their commonalities and distinctions. Each definition gives a criterion
quantified over states \(s\) that immediately follow call (or tail-call) steps.
If an execution can reach a state \(s'\) such that \(s' \stepstounder{\overline{\psi}} s\)
where \(\mathbf{call} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then \(s\) is the target
of a call. Likewise, if \(\mathbf{tailcall} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then
\(s\) is the target of a tailcall. As a shorthand, we write that each property is defined
by a criterion that must hold ``for all (tail)call targets \(s\).''

\(\wbcf\), \(\clri\), and \(\clec\) are each straightforward: they define predicates that must
hold on return from the call. \(\clrc\) and \(\clei\) both compare the execution of the
call state with that of a variant state, and are concerned with both their internal and
their return-time behavior. So, for some \(\nach\) that is an appropriate variant,
all states must fulfill an ``internal'' clause that their traces are similar,
and a ``return-time'' clause, that any potentially corrupted memory at their returns
is irrelevant.

\begin{table*}[h]
  \setlength{\tabcolsep}{1pt}
  \center
  \begin{tabular}{l r l l l}
    \rowcolor{black!20}
    1
    & \(\wbcf \triangleq\) & \(|\sigma| \uparrow \ret\)
    & \(\textnormal{ where } \ret ~ \mach' \triangleq \)
    \(\mach'[\SP] = \mach[\SP] \land \mach'[\PCname] = \mach[\PCname]+4\)
%    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is called}\) \\
    & \(\textnormal{ for all call targets } (\mach,(V,\sigma))\) \\
    %
    \rowcolor{black!10}
    2
    & \(\clri \triangleq\) & \((|\sigma| \uparrow \intProp) ~ (\mach,(V,\sigma))\)
    & \(\textnormal{ where } \intProp ~ \mach' \triangleq
    \mach' \parallel \sealed(V) \cap \Delta(\mach,\mach')\)
%    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is called}\) \\
    & \(\textnormal{ for all call targets } (\mach,(V,\sigma))\) \\
    %
    \rowcolor{black!20}
    3
    & \(\clrc \triangleq\) & \(\forall \nach \textnormal{ s.t. } \mach \approx_{\components} \nach,\)
    & \(\textnormal{ where } \components = \sealed(V)\)
%    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called}\) \\
    & \(\textnormal{ for all (tail)call targets } (\mach,(V,\sigma))\) \\
    \rowcolor{black!20}
    3a & & \(|\sigma| \hookrightarrow (\mach,(V,\sigma)) \simeq |\sigma| \hookrightarrow (\nach,(V,\sigma))\) & & \\
    \rowcolor{black!20}
    3b & & \(\textnormal{ and } (\mach,(V,\sigma)) ~ (|\sigma| \Uparrow \confProp) ~ (\nach,(V,\sigma))\)
    & \(\textnormal{ where } (\mach' ~ \confProp ~ \nach') \triangleq
    \mach' \parallel \bar{\Diamond}(\mach,\nach,\mach',\nach')\) & \\
    %
    \rowcolor{black!10}
    4
    & \(\clec \triangleq\) & \((|\sigma| \uparrow \cconfProp) ~ (\mach,(V,\sigma))\)
    & \(\textnormal{ where } \cconfProp ~ \mach' \triangleq
    \mach' \parallel \Delta(\mach,\mach') - \components\)
%    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called}\) \\
    & \(\textnormal{ for all (tail)call targets } (\mach,(V,\sigma))\) \\
    \rowcolor{black!10}
    & & & \(\textnormal{ where } \components = \public(V) \cup \object(V)\) & \\
    %
    \rowcolor{black!20}
    5
    & \(\clei \triangleq\) & \(\forall \nach \textnormal{ s.t. } \mach \approx_{\components} \nach,\)
    & \(\textnormal{ where } \components = \public(V) \cup \object(V)\)
%    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called}\) \\
    & \(\textnormal{ for all (tail)call targets } (\mach,(V,\sigma))\) \\
   \rowcolor{black!20}
    5a & & \(|\sigma| \hookrightarrow (\mach,(V,\sigma)) \simeq |\sigma| \hookrightarrow (\nach,(V,\sigma))\) & & \\
    \rowcolor{black!20}
    5b & & \(\textnormal{ and } (\mach,(V,\sigma)) ~ (|\sigma| \Uparrow \cintProp) ~ (\nach,(V,\sigma))\)
    & \(\textnormal{ where } (\mach' ~ \cintProp ~ \nach') \triangleq
    \mach' \parallel \bar{\Diamond}(\mach,\nach,\mach',\nach')\) & \\
  \end{tabular}
  \caption{Properties}
  \label{tab:props}
\end{table*}

@@

The system we've modeled so far has been very simple, but our properties
support an important dimension of generality: adding features. We now
briefly introduce the features of our primary testing machine.

The full machine defines additional operations, and extends some of the old ones.
We add a field \(\overline{sa}\) to the \(\mathbf{call}\) operation: a set of
triples of a register \(\reg\), a base offset \(\mathit{off}\), and a size \(sz\), denoting
that the value at the offset \(\mathit{off}\) from \(\reg\) is to be passed as an argument.
The new \(\mathbf{tailcall}\) operation has the same fields, but deals with tail-call
optimizations in which the callee will reuse the caller's stack. The \(\mathbf{alloc}\) operation
gains a boolen flag indicating whether the allocation is to be public, accessible to
all functions until deallocated. The rules are given in \cref{fig:advops}; the
rules in \cref{fig:basicops} can be recaptured by instantiating
\(\mathbf{call}\) with \(\overline{sa}\) as the empty set, and \(\mathbf{alloc}\)
with \(\mathbf{f}\).

\subsection{Sharing Stack Memory}
In our examples, we have presented a vision of stack safety in which
the interface between caller and callee is in the registers that pass
arguments and return values. This is frequently not the case in a realistic
setting. Arguments may be passed on the stack due to being spilled, as an implementation
of variadic arguments, or because they are reference objects that inherently have
pass-by-reference semantics. The caller may also take the address of a local object and
pass that as a pointer to its callee.

@@

In this mechanism, we can describe an argument being passed by their relative address
with the operation \(\mathbf{call} ~ \dots ~ (\SP, \mathit{off}, \mathit{sz})\).
In the case of pass-by-reference semantics, if the compiler designates register
\(\reg\) as holding the reference, then the operations is
\(\mathbf{call} ~ \dots ~ (\reg, 0, \mathit{sz})\).

In both cases, the immediate callee retains access to the passed object, but future
callees will not---unless the object is passed-by-reference further down the stack.
On the other hand, in the case of a caller explicitly taking the address of an
object and passing it as a pointer, we have no way obvious way to limit the scope
of such sharing.

Our primary machine treats this scenario as the caller allocating a ``public''
object that can be accessed by anyone until it's deallocated. We extend the
\(\mathbf{alloc}\) operation with a boolean flag, where {\bf t} indicates
that the allocation is public, and {\bf f} is private.
In the likely event that the space for multiple objects is allocated in a single step,
that step can make multiple allocation operations, each labeled appropriately.
Allocating public objects affects the call stack very similarly to private ones,
but instead of labeling them \(\object\) they become \(\public\), so they are
never sealed at a call (\cref{sfig:publicalloc}).

@@

Since the caller will not be returned to, it does not need integrity, though
it should still enjoy confidentiality. We set its frame to \(\unsealed\) rather
than \(\sealed\) to express this. Of course, some objects may be passed as arguments
in place, easily modeled by including them in \(\overline{sa}\). More sophisticated
behaviors may require sequences of {\bf dealloc}, {\bf tailcall}, then {\bf alloc}.

>>>>

\author{
  \IEEEauthorblockN{
    Sean Noble Anderson
  }
  \IEEEauthorblockA{
    Portland State University\\
    ander28@pdx.edu\\
  }
  \and
  \IEEEauthorblockN{
    Roberto Blanco
  }
  \IEEEauthorblockA{
    Max Planck Institute for Security and Privacy\\
    roberto.blanco@mpi-sp.org\\
  }
  \and
  \IEEEauthorblockN{
    Leonidas Lampropoulos
  }
  \IEEEauthorblockA{
    University of Maryland, College Park\\
    leonidas@umd.edu\\
  }
  \linebreakand
  \IEEEauthorblockN{
    Benjamin C. Pierce
  }
  \IEEEauthorblockA{
    University of Pennsylvania\\
    bcpierce@cis.upenn.edu\\
   }
  \and
  \IEEEauthorblockN{
    Andrew Tolmach
  }
  \IEEEauthorblockA{
    Portland State University\\
    tolmach@pdx.edu\\
  }
}

@@

\section{Formalization}
\label{sec:machine}

@@

We now give a formal description of our machine model, security semantics,
and properties. Our definitions abstract over the details of the target machine
architecture and ABI, the set of security-relevant operations, the rules that
govern evolution of the security context, the set of observable events, and
a notion of value compatibility.
\apt{Not quite true: the property definitions require a notion of
  call entry.}
\apt{Any more? Give a more listlike presentation?
  Need to clarify exactly what the parameters are, both in the initial
  presentation and in the various extensions, including the appendix.}

\subsection{Machine}
The building blocks of a machine are {\em words} and {\em registers}.
Words are ranged over by \(\word\) and, when used as addresses, \(\addr\),
and are drawn from the set \(\WORDS\).
Registers in the set \(\REGS\) are ranged over by \(\reg\), with the stack pointer
given the special name \(\SP\);
some registers may be classified as caller-saved or callee-saved.
Along with the program counter, \(\PCname\), these are referred to as
{\em state elements} \(\component\) in the set \(\COMPONENTS ::= \PCname | \WORDS | \REGS\).

A {\em machine state} \(\mach \in \MACHS\) is a map from state elements to a set \(\mathcal{V}\) of
\emph{values}.
Each value \(v\) contains a \emph{payload} word, written \(|v|\).
We write \(\mach[\component]\) to denote the value of \(\mach\) at
\(\component\)  and \(\mach[v]\) as shorthand for \(\mach[|v|]\).
The details of value structure depend on the specific machine being modelled;
intuitively, the payload represents the part of the value that is relevant to
the behavior of the basic machine, while the rest of the value may contain
information relevant to a hardware enforcement mechanism (such as a tag).
We assume a given \emph{compatibility} equivalence relation \(\sim\) on values,
and lift it element-wise to states.
Values are compatible if their non-payload information is identical, 
even though their payloads may differ.
\apt{This is still not very convincing!
  empting to say that only the payloads can affect the step function, but that is
  too strong, right? (OK for tags, but not, e.g. capabilities?}

The machine has a step function \(\mach \xrightarrow{\bar{\psi},\obs} \mach'\).
Except for the annotations over the arrow, this function just encodes the usual
ISA description of the machine's instruction set. The annotations serve to connect
the machine's operation to our security setting: 
\(\bar{\psi}\) is a list of security-relevant operations drawn from an assumed set \(\Psi\),
and \(\obs\) is an (potentially silent) observable event; these are described further below.

\subsection{Security semantics}

The security semantics operates in parallel with the 
Each state element (memory word or register) is given a \emph{security class} 
\(l \in \{\public, \object, \sealed, \unsealed\}\).
A \emph{view} \(V \in \mathit{VIEW}\) maps elements to security classes.
For any security class \(l\), we write \(l(V)\)
to denote the set of elements \(\component\) such that \(V ~ \component = l\).
The {\it initial view} \(V_0\) maps all stack locations to \(\unsealed\),
all other locations to \(\public\), and registers based on which set they
belong to: \(\sealed\) for callee-saved, \(\unsealed\) for caller-saved, and \(\public\) otherwise.
\apt{This doesn't quite match example, where there is magically an initial argument register labeled \(\active\).}

A (security) \emph{context} is
a pair of the current activation's view and
a list of views representing the call stack (pending inactive
principals), ranged over by \(\sigma\).
%
\[\context \in \CONTEXTS ::= \mathit{VIEW \times list ~ VIEW}\]
%
The initial context is \(\context_0 = (V_0, \emplist)\).

\cref{sec:example} describes informally how the security context evolves as the system performs
security-relevant operations. Formally, we combine each machine state with a context
to create a {\it combined state} \(s = (\mach,\context)\) and a lift the transition
to \(\stepstounder{}\) on combined states. 
At each step, the context updates based on the function
\(Op : \MACHS \rightarrow \CONTEXTS \rightarrow \psi \rightarrow \CONTEXTS\).
(Note that \(Op\) takes as its first argument the state {\it before} the step.)
Since a single step might correspond to multiple operations, we apply
\(Op\) as many times as needed, using \(\mathit{foldl}\).

@@

A definition of \(Op\) is most convenient to present decomposed into
rules for each operation. We have already seen the intuition behind the rules for
\(\mathbf{alloc}\), \(\mathbf{call}\), and \(\mathbf{ret}\).
For the machine described in the example, the \(Op\) rules would be those
found in \cref{fig:basicops}.

@@

We are particular interested in traces that end just after a function returns.
We define these in terms of the depth \(d\) of the security context's call stack \(\sigma\).
We write \(d \hookrightarrow s\) for the trace of execution from a state \(s\)
up to the first point where the stack depth is smaller than \(d\), defined
coinductively by these rules:

@@

\noindent
When \(d = 0\), the trace will always be infinite; in this case we
omit \(d\) and just write \(\hookrightarrow s\).

Two event traces $\obsT_1$ and $\obsT_2$ are {\em similar},
written \(\obsT_1 \eqsim \obsT_2\), if the sequence of non-silent events
is the same. That is, we compare up to deletion of \(\tau\) events.
\apt{Didn't we use to say something about the (arguably) odd nature of this definition?}

@@

\subsection{Variants, corrupted sets, and ``on-return'' assertions}
\label{sec:props}

Two (compatible) states are variants with respect to a set of elements \(\components\)
if they agree on the value of every element not in \(\components\). 
Our notion of non-interference involves comparing the traces of such
\(\components\)-variants. We use this to define sets of irrelevant elements,
and secrets in general.\apt{last phrase is cryptic}

\definition The \emph{difference set} of two machine states \(\mach\) and \(\mach'\), written \(\Delta(\mach,\mach')\),
is the set of elements \(\component\) such that \(\mach[\component] \not = \mach'[\component]\).

\definition Machine states \(\mach\) and \(\nach\) are {\em \(\components\)-variants},
written \(\mach \approx_\components \nach\), if \(\mach\sim\nach\) and
\(\Delta(\mach,\nach) \subseteq \components\). 
%if all \(\component \not \in \components\), \(\mach[\component] = \nach[\component]\)
%and for all \(\component \in \components\), \(\mach[\component] \sim \nach[\component]\).

\definition An element set \(\components\) is \emph{irrelevant} to state \((\mach,\context)\),
written \((\mach,\context) \parallel \components\), if for all
\(\nach\) such that \(\mach \approx_{\components} \nach\),
\(\hookrightarrow (\mach,\context)  \eqsim \hookrightarrow (\nach,\context)\).

@@

If we consider two execution sequences, one from \(\mach\) to \(\mach'\)
and the other from \(\nach\) to \(\nach'\),
then \(\bar{\Diamond}(\mach,\mach',\nach,\nach')\) is the set of elements that
change in one or both executions and end up with different values. Intuitively,
this captures the effect of any differences between \(\mach\) and \(\nach\), i.e.,
the set of values that are ``corrupted'' by those differences.

@@

\judgmenttwobrlong[Step]
                  {\(|\sigma| \geq d\)}
                  {\((d \uparrow P) ~ (\mach', \context')\)}
                  {\((\mach, (V,\sigma)) \stepstounder{\overline{\psi},\obs} (\mach', \context')\)}
                  {\((d \uparrow P) ~ (\mach, (V,\sigma))\)}

@@

\judgmenttwobrlong[Left]
                  {\(|\sigma_1| \geq d\)}
                  {\((\mach_1,(V_1,\sigma_1)) \stepstounder{\overline{\psi},\obs} (\mach_1',\context_1')\)}
                  {\((\mach_1',\context_1') ~ (d \Uparrow R) ~ (\mach_2,(V_2,\sigma_2))\)}
                  {\((\mach_1,(V_1,\sigma_1)) ~ (d \Uparrow R) ~ (\mach_2,(V_2,\sigma_2))\)}

\judgmenttwobrlong[Right]
                  {\(|\sigma_2| \geq d\)}
                  {\((\mach_2,(V_2,\sigma_2)) \stepstounder{\overline{\psi},\obs} (\mach_2',\context_2')\)}
                  {\((\mach_1,(V_1,\sigma_1)) ~ (d \Uparrow R) ~ (\mach_2',\context_2')\)}
                  {\((\mach_1,(V_1,\sigma_1)) ~ (d \Uparrow R) ~ (\mach_2,(V_2,\sigma_2))\)}

Finally, we can define our core properties. They can be found in \cref{tab:props},
arranged to show their commonalities and distinctions. Each definition gives a criterion
quantified over states \(s\) that immediately follow call (or tail-call) steps.
If an execution can reach a state \(s'\) such that \(s' \stepstounder{\overline{\psi}} s\)
where \(\mathbf{call} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then \(s\) is the target
of a call.
%Likewise, if \(\mathbf{tailcall} ~ \addr ~ \overline{\reg} \in \bar{\psi}\), then
%\(s\) is the target of a tailcall.
As a shorthand, we write that each property is defined
by a criterion that must hold ``for all call targets \(s\).''

\(\wbcf\), \(\clri\), and \(\clec\) are each straightforward: they define predicates that must
hold on return from the call. \(\clrc\) and \(\clei\) both compare the execution of the
call state with that of a variant state, and are concerned with both their internal and
their return-time behavior. So, for some \(\nach\) that is an appropriate variant,
all states must fulfill an ``internal'' clause that their traces are similar,
and a ``return-time'' clause, that any potentially corrupted memory at their returns
is irrelevant.
\apt{This paragraph needs major expansion, to paraphrase the definitions informally,
  and TO SAY MUCH MORE ABOUT THE CALLEE PROPERTIES, which are not intuitive at all (to me)!}

\begin{table*}[h]
  \setlength{\tabcolsep}{1pt}
  \center
  \begin{tabular}{l r l l l}
    \rowcolor{black!20}
    1
    & \(\wbcf \triangleq\) & \((|\sigma| \uparrow \ret) ~ ????\)
    & \(\textnormal{ where } \ret ~ \mach' \triangleq \)
    \(\mach'[\SP] = \mach[\SP] \land \mach'[\PCname] = \mach[\PCname]+4\)
%    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is called}\) \\
    & \(\textnormal{ for all call targets } (\mach,(V,\sigma))\) \\
    %
    \rowcolor{black!10}
    2
    & \(\clri \triangleq\) & \((|\sigma| \uparrow \intProp) ~ (\mach,(V,\sigma))\)
    & \(\textnormal{ where } \intProp ~ \mach' \triangleq
    \mach' \parallel (\sealed(V) \cap \Delta(\mach,\mach'))\)
%    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is called}\) \\
    & \(\textnormal{ for all call targets } (\mach,(V,\sigma))\) \\
    %
    \rowcolor{black!20}
    3
    & \(\clrc \triangleq\) & \(\forall \nach \textnormal{ s.t. } \mach \approx_{\components} \nach,\)
    & \(\textnormal{ where } \components = \sealed(V)\)
%    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called}\) \\
    & \(\textnormal{ for all call targets } (\mach,(V,\sigma))\) \\
    \rowcolor{black!20}
    3a & & \(|\sigma| \hookrightarrow (\mach,(V,\sigma)) \simeq |\sigma| \hookrightarrow (\nach,(V,\sigma))\) & & \\
    \rowcolor{black!20}
    3b & & \(\textnormal{ and } (\mach,(V,\sigma)) ~ (|\sigma| \Uparrow \confProp) ~ (\nach,(V,\sigma))\)
    & \(\textnormal{ where } (\mach' ~ \confProp ~ \nach') \triangleq
    \mach' \parallel \bar{\Diamond}(\mach,\nach,\mach',\nach')\) & \\
    %
    \rowcolor{black!10}
    4
    & \(\clec \triangleq\) & \((|\sigma| \uparrow \cconfProp) ~ (\mach,(V,\sigma))\)
    & \(\textnormal{ where } \cconfProp ~ \mach' \triangleq
    \mach' \parallel (\Delta(\mach,\mach') - \components)\)
%    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called}\) \\
    & \(\textnormal{ for all call targets } (\mach,(V,\sigma))\) \\
    \rowcolor{black!10}
    & & & \(\textnormal{ where } \components = \public(V) \cup \object(V)\) & \\
    %
    \rowcolor{black!20}
    5
    & \(\clei \triangleq\) & \(\forall \nach \textnormal{ s.t. } \mach \approx_{\components} \nach,\)
    & \(\textnormal{ where } \components = \public(V) \cup \object(V)\)
%    & \(\textnormal{ when } (\mach,(V,\sigma)) \textnormal{ is (tail)called}\) \\
    & \(\textnormal{ for all call targets } (\mach,(V,\sigma))\) \\
   \rowcolor{black!20}
    5a & & \(|\sigma| \hookrightarrow (\mach,(V,\sigma)) \simeq |\sigma| \hookrightarrow (\nach,(V,\sigma))\) & & \\
    \rowcolor{black!20}
    5b & & \(\textnormal{ and } (\mach,(V,\sigma)) ~ (|\sigma| \Uparrow \cintProp) ~ (\nach,(V,\sigma))\)
    & \(\textnormal{ where } (\mach' ~ \cintProp ~ \nach') \triangleq
    \mach' \parallel \bar{\Diamond}(\mach,\nach,\mach',\nach')\) & \\
  \end{tabular}
  \caption{Properties\apt{In WBCF, surely we need a state arg? But it needs to be the state \emph{before} the call,
      doesn't it?}}
  \label{tab:props}
\end{table*}

@@

The system we've modeled so far has been very simple, but our properties
support an important dimension of generality: adding features.\apt{Just what needs to be changed
to add these features?}
We now briefly introduce the features of our primary testing machine.\apt{Make sure
testing has been introduced properly before now. And why ``primary''?}

The full machine defines additional operations, and extends some of the old ones.
We add a field \(\overline{sa}\) to the \(\mathbf{call}\) operation: a set of
triples of a register \(\reg\), a base offset \(\mathit{off}\), and a size \(sz\), denoting
that the value at the offset \(\mathit{off}\) from \(\reg\) is to be passed as an argument.
The new \(\mathbf{tailcall}\) operation has the same fields, but deals with tail-call
optimizations in which the callee will reuse the caller's stack. The \(\mathbf{alloc}\) operation
gains a boolen flag indicating whether the allocation is to be public, accessible to
all functions until deallocated. The rules are given in \cref{fig:advops}; the
rules in \cref{fig:basicops} can be recaptured by instantiating
\(\mathbf{call}\) with \(\overline{sa}\) as the empty set, and \(\mathbf{alloc}\)
with flag \(\mathbf{f}\).

\subsection{Sharing Stack Memory}
In our examples, we have presented a vision of stack safety in which
the interface between caller and callee is in the registers that pass
arguments and return values. This is frequently not the case in a realistic
setting. Arguments may be passed on the stack (e.g. because there are too many
to pass in registers), as an implementation
of variadic arguments, or because they are reference objects \apt{??} that inherently have
pass-by-reference semantics. The caller may also take the address of a local object and
pass that as a pointer to its callee.

@@

Using this mechanism, we can describe an argument being passed on the stack
by giving its \(\SP\)-relative offset,
with the operation \(\mathbf{call} ~ \dots ~ (\SP, \mathit{off}, \mathit{sz})\).
In the case of pass-by-reference semantics, if the compiler designates register
\(\reg\) as holding the reference, then the operations is
\(\mathbf{call} ~ \dots ~ (\reg, 0, \mathit{sz})\).\apt{This is unclear to me. 
  The compiler knows where the cbr parameter lives in the caller's stack
  frame, so why wouldn't it use a sp-relative spec for that too? Does it have
  to do with passing a CBR parameter further down to another callee as you allude
  to in the next para?}

In both cases, the immediate callee retains access to the passed object, but deeper
callees will not---unless the object is passed-by-reference further down the stack.
On the other hand, in the case of a caller explicitly taking the address of an
object and passing it as a pointer, we have no way obvious way to limit the scope
of such sharing.

Our primary \apt{again...} machine treats this scenario as the caller allocating a ``public''
object that can be accessed by anyone until it's deallocated. We extend the
\(\mathbf{alloc}\) operation with a boolean flag, where {\bf t} indicates
that the allocation is public, and {\bf f} is private.
In the likely event that the space for multiple objects is allocated in a single step,
that step can make multiple allocation operations, each labeled appropriately.
Allocating public objects affects the call stack very similarly to private ones,
but instead of labeling them \(\object\) they become \(\public\), so they are
never sealed at a call (\cref{sfig:publicalloc}).

@@

Since the caller will not be returned to, it does not need integrity, though
it should still enjoy confidentiality. We set its frame to \(\unsealed\) rather
than \(\sealed\) to express this. Of course, some objects may be passed as arguments
in place\apt{??}, easily modeled by including them in \(\overline{sa}\). More sophisticated
behaviors may require sequences of {\bf dealloc}, {\bf tailcall}, then {\bf alloc}.

### 2023-02-02 submission5/ideas-v1.tex
pass through formalism

Whatever the mechanism for labeling transitions, we get a base
machine transition \(\mach \xrightarrow{\bar{\psi}, \obs} \mach'\), where \(\obs\) is
an event (see below) and \(\bar{\psi}\) is a list of security-relevant operations.
We then lift this into a transition between pairs of machine states and contexts,
\((\mach,\context) \stepstounder{\overline{\psi},\obs} (\mach', \context')\).

>>>>

Whatever the mechanism for labeling transitions, we get a base
machine transition \(\mach \xrightarrow{\bar{\psi}, \obs} \mach'\), where \(\obs\) is
an event (see below) and \(\bar{\psi}\) is a list of security-relevant operations.
\apt{Example doesn't include the event annotation. Should remove here, or add a note there.}
We then lift this into a transition between pairs of machine states and contexts,
\((\mach,\context) \stepstounder{\overline{\psi},\obs} (\mach', \context')\).\apt{We don't need this notation for the example.}
